Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-03-30 paper/AlignedIsotropicGW.tex
Fixed #4.

We fit hierarchical models of the three LIGO O1 observations using
these six different, zero-parameter population distributions (see
Section \ref{sec:hierarchical}).  We also fit three mixture models for
the population, where the spin magnitude distribution is fixed but the
angular distribution is a weighted sum of the isotropic and aligned
distribution.  The evidence, or marginal likelihood, for each of the
models is shown in Figure \ref{fig:O1-odds}.  For all three magnitude
distributions, the mixture models' posterior on the mixing fraction
peaks at 100\% isotropic, which explains why the zero-parameter,
pure-isotropic models are preferred over the single-parameter mixture
models for every magnitude distribution with this data set.  Not
surprisingly, given the small $\chieff$ values in the three detected
systems, the most-favoured model among those with an isotropic angular
distribution has the ``low'' magnitude distribution; the most favoured
model among those with an aligned distribution also has the ``low''
magnitude distribution.  The odds ratio between the ``low'' aligned
and ``low'' isotropic models is $\OOneOddsIsoAligned$, or
$\OOneSigmaIsoAligned\sigma$; thus the data favour isotropic spins
among our suite of models.  While the data favour spin amplitude
distributions with small spin magnitudes, note that a model with all
\ac{BBH} systems having zero spin is ruled out by the GW151226
measurements, which bound $\chieff \gtrsim 0.1$ at 90\% credibility
\citep{2016PhRvL.116x1103A}.

>>>>

We fit hierarchical models of the three LIGO O1 observations using
these six different, zero-parameter population distributions (see
Section \ref{sec:hierarchical}).  We also fit three mixture models for
the population, where the spin magnitude distribution is fixed but the
angular distribution is a weighted sum of the isotropic and aligned
distribution.  The evidence, or marginal likelihood, for each of the
models is shown in Figure \ref{fig:O1-odds}.  For all three magnitude
distributions, the mixture models' posterior on the mixing fraction
peaks at 100\% isotropic, which explains why the zero-parameter,
pure-isotropic models are preferred over the single-parameter mixture
models for every magnitude distribution with this data set.  Not
surprisingly, given the small $\chieff$ values in the three detected
systems, the most-favoured model among those with an isotropic angular
distribution has the ``low'' magnitude distribution; the most favoured
model among those with an aligned distribution also has the ``low''
magnitude distribution.  The odds ratio between the ``low'' aligned
and ``low'' isotropic models is $\OOneOddsIsoAligned$, or
$\OOneSigmaIsoAligned\sigma$; thus the data favour isotropic spins
among our suite of models.  While the data favour spin amplitude
distributions with small spin magnitudes, note that a model with all
\ac{BBH} systems having zero spin is ruled out by the GW151226
measurements, which bound at least one black hole to have spin
magnitude $\geq 0.2$ at 90\% credibility \citep{2016PhRvL.116x1103A}.
